% \documentclass[12pt,twocolumn]{article}
% Copernicus stuff
\documentclass[gmd,manuscript]{copernicus}

% page/line labeling and referencing
% from http://goo.gl/HvS9BK
% \newcommand{\pllabel}[1]{\label{p-#1}\linelabel{l-#1}}
% \newcommand{\plref}[1]{page~\pageref{p-#1}, line~\lineref{l-#1}}
% answer environment for reviewer responses
% \newenvironment{answer}{\color{blue}}{}

\runningtitle{WIP Paper Draft \today}
\runningauthor{Balaji et al.}

\begin{document}

\title{Requirements for a global data infrastructure in support of CMIP6}
% \pllabel{SC1-1}

\Author[1,4]{V.}{Balaji}
\Author[2]{E.}{Maisonnave}
\Author[3,4]{N.}{Zadeh}
\Author[5,6]{B. N.}{Lawrence}
\Author[7]{J.}{Biercamp}
\Author[8]{U.}{Fladrich}
\Author[9,10]{G.}{Aloisio}
\Author[4]{R.}{Benson}
\Author[11]{A.}{Caubel}
\Author[3,4]{J.}{Durachta}
\Author[12]{M.-A.}{Foujols}
\Author[6]{G.}{Lister}
\Author[9]{S.}{Mocavero}
\Author[3,4]{S.}{Underwood}
\Author[3,4]{G.}{Wright}

% \Author[10]{Richard}{Loft}

\affil[1]{Princeton University, Cooperative Institute of Climate
  Science, Princeton NJ, USA}
\affil[2]{Centre Europ\'een de Recherche Avanc\'ee en Calcul
  Scientifique (CERFACS), Toulouse, France}
\affil[3]{Engility Inc., Dover NJ, USA}
\affil[4]{NOAA/Geophysical Fluid Dynamics Laboratory, Princeton NJ, USA}
\affil[5]{National Centre for Atmopheric Science and University of
  Reading, UK}
\affil[6]{Science and Technology Facilities Council, Abingdon, UK}
\affil[7]{Deutsches Klimarechenzentrum GmbH, Hamburg, Germany}
\affil[8]{Swedish Meteorological and Hydrological Institute,
  Norrk\"oping, Sweden}
\affil[9]{Centro Euro-Mediterraneo sui Cambiamenti Climatici (CMCC)
Foundation, Lecce, Italy}
\affil[10]{University of Salento, Lecce, Italy}
\affil[11]{Laboratoire des Sciences du Climat et de l’Environnement
  LSCE/IPSL, CEA-CNRS-UVSQ, Université Paris-Saclay, 91191
  Gif-sur-Yvette Cedex, France}
\affil[12]{Institut Pierre-Simon Laplace, CNRS/UPMC, Paris, France}
% \affil[10]{NCAR}

\correspondence{V. Balaji (\texttt{balaji@princeton.edu})}

% \author{V. Balaji\thanks{Corresponding author: Princeton University,
%     201 Forrestal Road, Princeton NJ 08540, USA.
%     Email:  \texttt{balaji@princeton.edu}}
%   \and Rusty Benson\thanks{NOAA/GFDL}
%   \and Bruce Wyman\footnotemark[2]
%   \and Isaac Held\footnotemark[2]}

\received{}
\pubdiscuss{} %% only important for two-stage journals
\revised{}
\accepted{}
\published{}

%% These dates will be inserted by Copernicus Publications during the typesetting process.


\firstpage{1}

\maketitle

% \pagebreak
\abstract{
}
% \pagebreak

\section{Introduction}
\label{sec:intro}


\begin{acknowledgements}
  V. Balaji is supported by the Cooperative Institute for Climate
  Science, Princeton University, Award NA08OAR4320752 from the
  National Oceanic and Atmospheric Administration, U.S. Department of
  Commerce. The statements, findings, conclusions, and recommendations
  are those of the authors and do not necessarily reflect the views of
  Princeton University, the National Oceanic and Atmospheric
  Administration, or the U.S. Department of Commerce. He is grateful
  to the Institut Pierre et Simon Laplace (LABEX-LIPSL) for support in
  2015 during which drafts of this paper were written.

  The research leading to these results has received funding from the
  European Union Seventh Framework program under the IS-ENES2 project
  (grant agreement No. 312979).

  B.N. Lawrence acknowledges additional support from the UK Natural
  Environment Research Council.

  We thank Lucas Harris and Ron Stouffer of NOAA/GFDL, as well as
  Claire Levy of IPSL and an anonymous reviewer, for insightful and
  thorough reviews of this article, down to the last comma.
\end{acknowledgements}

\bibliographystyle{copernicus}
\bibliography{refs}
\end{document}
